Adaptive Disk Storage for Interaction Graphs

### 2014-04-30 notes/graph-adapt/main.tex
added algorithm for partitioning with overlapping

>>>>

\begin{itemize}

\item First, let's define a measure for the similarity between two
partitions. I think this can be the sum of the size of attributes that
they do not have in common. So, if we have partitions: abc, abd, and
abe, then abc-abd will be more similar than abc-abe, if size(d) <
size(e).

\item The first partitioning is based on what queries we have seen.
Every query gets its own sub-block. This is the "ideal" situation,
because the I/O cost would be minimized for every query that we would
have seen.

\item We calculate the storage cost for the partitioning.

\item If the storage cost is above some threshold, then we do a pairwise
comparison of all sub-blocks to determine which two are the most
similar, using (0).

\item We combine the two most-similar sub-blocks, and repeat the process
starting at (2) until we are satisfied with the storage cost.

\item The result is our partitioned block.

\end{itemize}
